Hochschild cohomology of torus-equivariant D-modules

### 2015-05-20 paper.tex
Use the new article class.
Add abstract from thesis.

\documentclass[english]{short-notes}

@@

>>>>

\documentclass[english]{ck-article}

@@

\begin{abstract}
    This article is dedicated to understanding the support theory (in the sense of \cite{BensonIyengarKrause:2008:LocalCohomologyAndSupportForTriangulatedCategories}) of equivariant D-modules.
    We discuss how to compute the Hochschild cohomology of the category of D-modules on a quotient stack via a relative compactification of the diagonal morphism.
    We then apply this construction to the case of torus-equivariant D-modules and describe the Hochschild cohomology as the cohomology of a D-module on the loop space of the quotient stack.
\end{abstract}
